---
title: 'Experiment 4: summa with time pressure'
output: rmarkdown::github_document
#output:
  #html_document: default
  #pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(tidyverse)
library(lme4)
library(languageR)
library(brms)

library("wesanderson")
source("helpers.R")
options(scipen=999)

theme_set(theme_bw())
key_col = wes_palette("Moonrise3")
cond_col = wes_palette("Royal2")
hist_col = wes_palette("Moonrise3")[1]
age_col = wes_palette("GrandBudapest1")

df = read.csv("../data/results_formatted.csv", header = TRUE)
demo = read.csv("../data/subject_info_merged.csv", header = TRUE)

#add column for lag response time
df$logRT = log(df$rawRT)

df$rt = df$rawRT
#df$rt = df$logRT
```
### Before Exclusions
**Number of participants tested:**
```{r before_exclusion, echo=FALSE}
length(demo$workerid)
```
**Participants in each condition:**
```{r before_exclusion_2, echo=FALSE}
workers = df %>%
  filter(slide_type == "practice_trial")
table(workers$Answer.condition) /4
```

### Exclusions

**Non-unique participants (remove all attempts):**
```{r not_unique_exclude, echo=FALSE}
not_unique = demo$workerid[duplicated(demo$workerid)]
not_unique

#remove non-unique
df = df[!(df$workerid %in% not_unique),]
demo = demo[!(demo$workerid %in% not_unique),]
```

**Participants whose native language is not english:**
```{r lang_exclude, echo=FALSE}
lang_exclude = demo %>%
  select(workerid, language) %>%
  unique() %>%
  filter(str_detect(language,regex("english", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("eng", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("egnlish", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("United States", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("en", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("ernglish", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("rnglish", ignore_case=TRUE),negate=TRUE))

lang_exclude

lang_exclude = lang_exclude %>%
  select(workerid)

df = df[!(df$workerid %in% lang_exclude$workerid),]
```
**Participants who got at least three practice trials wrong:**
```{r practice_exclude, echo=FALSE}
practice = df %>% 
  filter(str_detect(slide_type,"practice_trial")) %>%
  mutate(WrongAnswer = ((audio=="none.wav" & image=="13" & key=="Yes")|(audio=="all.wav" & image=="13" & key=="No")|(audio=="all.wav" & image=="0" & key=="Yes")| (audio=="none.wav" & image=="0" & key=="No"))) %>% 
  group_by(workerid) %>% 
  count(WrongAnswer) %>% 
  filter(WrongAnswer == TRUE & n>2)

table(practice$n)

df = df[!(df$workerid %in% practice$workerid),]
```
**Participants who got the audio check wrong more than one once:**
```{r audio_exclude, echo=FALSE}
audio_fail = df %>%
  filter(str_detect(slide_type,"audio_check")) %>%
  mutate(WrongAnswer = key != "Four") %>%
  group_by(workerid) %>% 
  count(WrongAnswer) %>%
  filter(WrongAnswer == TRUE & n>1)

table(audio_fail$workerid)

df = df[!(df$workerid %in% audio_fail$workerid ),]
```
**Participants who got the second comprehension question wrong more than twice:**
```{r comp_exclude, echo=FALSE}
comp1_fail = df[df$slide_type=="comprehension_check_1" & ((df$Answer.condition=="all_QUD" & df$key!="Empty") | (df$Answer.condition=="any_QUD" & df$key!="Jam")),]
comp2_fail = df[df$slide_type=="comprehension_check_2" & ((df$Answer.condition=="all_QUD" & df$key!="Empty") | (df$Answer.condition=="any_QUD" & df$key!="Jam")),]

#table(comp1_fail$workerid)
#table(comp2_fail$workerid)

comp2_fail =  comp2_fail %>%
  group_by(workerid) %>%
  count() %>%
  filter(n>2)

comp2_fail

df = df[!(df$workerid %in% comp2_fail$workerid ),]
```
**Participants with accuracy of lower than 85% on non-critical trials with "some","none","all" and numbers below 6:**
```{r accuracy_exclude, echo=FALSE}
yes_list = c("summa2","summa5","summa8","summa11",
             "all13",
             "none0",
             "zero0","two2","five5","eight8","eleven11","thirteen13")

exclude_list = c("seven11","eight8","eight13","nine5","ten5","ten13","eleven0","eleven8","eleven11","twelve2","thirteen8")

accuracy = df %>% 
  filter(str_detect(slide_type,"trial")) %>% 
  filter(str_detect(slide_type,"practice", negate = TRUE)) %>%
  mutate(concat = str_c(str_sub(audio,1,end=-5),image)) %>%
  filter(str_detect(concat,"summa13", negate = TRUE)) %>%
  filter(!key=="Late") %>%
  filter(!concat %in% exclude_list) %>%
  mutate(rightAnswer = ifelse(concat %in% yes_list,"Yes","No")) %>%
  mutate(gaveRightAnswer = ifelse(key==rightAnswer,"1","0"))

answerNumber = accuracy %>%
  group_by(workerid) %>%
  count(workerid) %>%
  mutate(answerNm = n)

low_accuracy = accuracy %>%
  group_by(workerid,gaveRightAnswer) %>%
  count(gaveRightAnswer) %>%
  merge(answerNumber[ ,c("workerid","answerNm")], by="workerid",all.x=TRUE) %>%
  #mutate(accuracy=ifelse(gaveRightAnswer=="1",n*100/64,0)) %>%
  mutate(accuracy=ifelse(gaveRightAnswer=="1",n*100/answerNm,0)) %>%
  filter(gaveRightAnswer=="1") %>%
  filter(accuracy < 85)

low_accuracy

df = df[!(df$workerid %in% low_accuracy$workerid),]
```
#### Additional Exclusions
**Participants who gave more than 5 very slow (logRT>20) responses:**
```{r slowworker_exclude, echo=FALSE}
slow_workers = df %>%
  filter(str_detect(slide_type,"trial")) %>% 
  filter(str_detect(slide_type,"practice", negate = TRUE)) %>% 
  mutate(slowResponse = logRT>30) %>%
  group_by(workerid) %>%
  count(slowResponse) %>%
  filter((slowResponse == TRUE)&(n>5))
slow_workers
  
df = df[!(df$workerid %in% slow_workers$workerid),]
```
**Responses that are faster than the onset of the quantifier (rawRT<600):**
```{r fast_trial_exclude, echo=FALSE}
fast = df %>%
  filter((slide_type=="trial_1"|slide_type=="trial_2") & rawRT<600)
nrow(fast)

fast = fast %>%
  select(X)

df = df[!(df$X %in% fast$X),]
```

**Responses that are very slow (logRT>20):**
```{r slow_trial_exclude, echo=FALSE}
slow = df %>%
  filter((slide_type=="trial_1"|slide_type=="trial_2") & logRT>20)
nrow(slow)

slow = slow %>%
  select(X)

df = df[!(df$X %in% slow$X),]
```
## After Exclusions
**Number of participants:**
```{r after_exclusions, echo=FALSE}
length(unique(df$workerid))
```
**Participants left in each condition:**
```{r after_exclusions_2, echo=FALSE}
workers = df %>%
  filter(slide_type == "practice_trial")
table(workers$Answer.condition) /4
```

## General
**Expected number of yes and no answers:**
```{r accuracy, echo=FALSE}
table(accuracy$rightAnswer)
```

**Accuracy**

```{r accuracy_2, echo=FALSE, fig.height=3, fig.width=4}
ggplot(accuracy,aes(x=key, fill=factor(gaveRightAnswer)))+
  geom_bar() +
  scale_fill_manual(values=c(hist_col,cond_col[4])) +
  xlab("response") +
  labs(fill="correct answer") 
  
```

**Accuracy and trial order**

```{r trial_order, echo=FALSE, fig.height=3, fig.width=5}
acc_prop = accuracy %>%
  group_by(workerid,slide_type) %>%
  summarise(proportion=mean(as.numeric(gaveRightAnswer))) %>%
  mutate(slide_type_rename = ifelse(slide_type=="trial_1","first_half", ifelse(slide_type=="trial_2", "second_half", slide_type)))

ggplot(acc_prop,aes(x=workerid, y=proportion, color=slide_type_rename))+
  geom_point() +
  geom_hline(yintercept = .85) +
  labs(color='trial order') +
  scale_color_manual(values=c(cond_col[3],hist_col))

```


**Distribution of RT and logRT**

```{r rt_distribution, echo=FALSE, fig.height=3, fig.width=10}
trials = df %>%
  filter(str_detect(slide_type,"trial")) %>% 
  filter(str_detect(slide_type,"practice", negate = TRUE))

ggplot(trials, aes(x=rawRT)) +
  geom_histogram(fill= hist_col,binwidth = 50) +
  scale_x_continuous(breaks=seq(0,10000,400),limits=c(0,10000)) +
  xlab("raw RT")

ggplot(trials, aes(x=logRT)) +
  geom_histogram(fill= hist_col,breaks=seq(0, 20, by=0.2)) +
  xlab("log transformed rt")
```
15 fastest responses (raw RT)
```{r fastest_resp, echo=FALSE}
head(sort(trials$rawRT),15)
```

15 slowest responses (raw RT)
```{r slowest_resp, echo=FALSE}
tail(sort(trials$rawRT),15)
```

###Non-critical Trials

**Response type:**

```{r non_critical, echo=FALSE}
non_critical = trials %>%
  mutate(concat = str_c(str_sub(audio,1,end=-5),image)) %>%
  filter(str_detect(concat,"summa13", negate = TRUE)) %>%
  #filter(workerid %in% low_accuracy$workerid) %>%
  group_by(audio,image,key) %>%
  summarize(Median=median(logRT),Mean=mean(logRT),CILow=ci.low(logRT),CIHigh=ci.high(logRT),SD=sd(logRT),Var=var(logRT),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(audio = fct_relevel(audio,"none.wav","all.wav","summa.wav","one.wav","two.wav","three.wav","four.wav","five.wav","seven.wav","eight.wav","nine.wav","ten.wav","eleven.wav","twelve.wav"))

ggplot(non_critical,aes(x=image, y=count ,fill=key))+
  geom_bar(stat = "identity", position=position_dodge(.9)) +
  scale_fill_manual(values=key_col) +
  ylab("count") +
  labs(fill="response") +
  facet_wrap(~audio, scales="free_x")
```

**Response time:**

```{r non_critical_2, echo=FALSE, fig.height=10, fig.width=13}
ggplot(non_critical,aes(x=image, y=Mean ,fill=key))+
  geom_bar(stat = "identity", position=position_dodge(.9)) +
  scale_fill_manual(values=key_col) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25,position=position_dodge(.9)) +
  ylab("mean logRT") +
  labs(fill="response") +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  facet_wrap(~audio, scales="free_x")
```

###Critical Trials
**Total number of critical trials (8 per participant):**
```{r critical, echo=FALSE}
critical = df %>% 
  filter(str_detect(slide_type,"trial")) %>% 
  filter(str_detect(slide_type,"practice", negate = TRUE))  %>%
  filter(str_detect(audio,"summa.wav")) %>%
  filter(str_detect(image,"13")) %>%
  droplevels()

nrow(critical) #6075
```

**Total number of critical trials with late responses removed:**
```{r critical2, echo=FALSE}
critical = df %>% 
  filter(str_detect(slide_type,"trial")) %>% 
  filter(str_detect(slide_type,"practice", negate = TRUE))  %>%
  filter(str_detect(audio,"summa.wav")) %>%
  filter(str_detect(image,"13")) %>%
  filter(str_detect(key,"Late", negate = TRUE)) %>%
  droplevels()

nrow(critical) #6075
```
  

####Response Type

```{r response_type, echo=FALSE, fig.height=3, fig.width=3}
rtype = critical %>%
  mutate(semantic = ifelse(key=="Yes",1,0)) %>%
  group_by(Answer.condition) %>%
  summarise(Proportion=mean(semantic),CILow=ci.low(semantic),CIHigh=ci.high(semantic)) %>%
  ungroup() %>%
  mutate(YMin=Proportion-CILow,YMax=Proportion+CIHigh)

ggplot(rtype, aes(x = Answer.condition, y=Proportion)) +
  geom_bar(stat="identity", fill = cond_col[4]) +
  geom_errorbar(aes(ymin=YMin, ymax=YMax, width=.25)) +
  ylab("Proportion of semantic responses") +
  xlab("")

rtype2 = critical %>%
  mutate(semantic = ifelse(key=="No",1,0)) %>%
  group_by(Answer.condition) %>%
  summarise(Proportion=mean(semantic),CILow=ci.low(semantic),CIHigh=ci.high(semantic)) %>%
  ungroup() %>%
  mutate(YMin=Proportion-CILow,YMax=Proportion+CIHigh)

pragmatic = ggplot(rtype2, aes(x = Answer.condition, y=Proportion)) +
  geom_bar(stat="identity", fill = cond_col[4]) +
  geom_errorbar(aes(ymin=YMin, ymax=YMax, width=.25)) +
  ylab("Proportion of pragmatic responses") +
  xlab("")

#pragmatic

#ggsave(pragmatic, file="../graphs/proportion_pragmatic.pdf",width=4,height=5)


```

**Distribution of participants over number of semantic responses**

```{r response_type_semantic, echo=FALSE, fig.height=3, fig.width=6}
d = critical %>%
  #modify_if(is.integer, as.factor) %>%
  group_by(workerid,key,.drop=FALSE) %>%
  count() %>% 
  filter(key=="Yes") %>%
  merge(critical[ ,c("workerid","Answer.condition")], by="workerid",all.x=TRUE) %>%
  unique() %>%
  mutate()

table(d$Answer.condition,d$n)

count = ggplot(d, aes(x=n,fill=Answer.condition)) +
  scale_fill_manual(values = cond_col) +
  geom_histogram(position=position_dodge(.5), bins=10, binwidth = 0.3) +
  xlab("Number of semantic responses") +
  labs(fill="QUD") +
  scale_x_continuous(breaks=c(0:8))

count

#ggsave(count, file="../graphs/count_pragmatic.pdf",width=4,height=5)

```

**Response type and trial order**

```{r response_type_time, echo=FALSE, fig.height=3, fig.width=6}
rtype = critical %>%
  mutate(semantic = ifelse(key=="Yes",1,0)) %>%
  group_by(Answer.condition,slide_type) %>%
  summarise(Proportion=mean(semantic),CILow=ci.low(semantic),CIHigh=ci.high(semantic)) %>%
  ungroup() %>%
  mutate(YMin=Proportion-CILow,YMax=Proportion+CIHigh) %>%
  mutate(slide_type_rename = ifelse(slide_type=="trial_1","first_half", ifelse(slide_type=="trial_2", "second_half", slide_type)))

ggplot(rtype, aes(x = Answer.condition, y=Proportion,fill=Answer.condition)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values = cond_col) +
  geom_errorbar(aes(ymin=YMin, ymax=YMax, width=.25)) +
  ylab("Proportion of semantic responses") +
  xlab("") +
  facet_wrap(~slide_type_rename) +
  labs(fill="QUD")
```

**Age distribution of participants**

```{r age_distribution, echo=FALSE, fig.height=3, fig.width=6}
demo2 = demo %>%
  group_by(age) %>%
  count() %>%
  filter(age != "") %>%
  filter(age != "male") %>%
  filter(age != "30-something")

ggplot(demo2,aes(x=age, y=n))+
  geom_bar(stat="identity", fill = hist_col)

```

**Response type and age**

```{r response_type_age, echo=FALSE}
demo$age = as.numeric(as.character(demo$age))

rtype = critical %>%
  mutate(semantic = ifelse(key=="No",1,0)) %>%
  left_join(demo,by = c("workerid")) %>%
  #mutate(age_bucket=ifelse(age<=25,"0-25",ifelse(age<=30,"26-30",ifelse(age<=35,"31-35",ifelse(age<=40,"36-40",ifelse(age<=44,"41-44",ifelse(age>44,"45+", NA))))))) %>%
  mutate(age_bucket = ifelse(age<=25,"18-25",ifelse(age<44,"26-44", ifelse(age>44,"45+",NA))))%>%
  group_by(Answer.condition,age_bucket) %>%
  summarise(Proportion=mean(semantic),CILow=ci.low(semantic),CIHigh=ci.high(semantic),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Proportion-CILow,YMax=Proportion+CIHigh) %>%
  #mutate(Answer.condition = fct_relevel(Answer.condition,"no_QUD","any_QUD")) %>%
  filter(!age_bucket == "NA") %>%
  filter(!age_bucket == "26-44")

age_pragmatic  = ggplot(rtype, aes(x = Answer.condition, y=Proportion, fill=Answer.condition)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values = cond_col) +
  geom_errorbar(aes(ymin=YMin, ymax=YMax, width=.25)) +
  ylab("Proportion of pragmatic responses") +
  xlab("") +
  labs(fill="QUD") +
  theme(legend.position = "none") +
  facet_wrap(~age_bucket) +
  #geom_text(aes(label=count),nudge_x=0.2)
  geom_text(aes(label=count, y = 0),position=position_dodge(width=1),vjust=0,size=3)

age_pragmatic

#ggsave(age_pragmatic, file="../graphs/age_pragmatic.pdf",width=6,height=3)

```

####Response Time

**Distribution of response times in critical trials**

```{r response_time, echo=FALSE, fig.height=3, fig.width=9}
ggplot(critical, aes(x=rawRT)) +
  geom_histogram(fill = hist_col, binwidth = 50) +
  scale_x_continuous(breaks=seq(0,10000,400),limits=c(0,10000)) +
  xlab("raw RT")
```

**Response time and QUD**

```{r response_time_qud, echo=FALSE, fig.height=3, fig.width=5}
agr = critical %>%
  group_by(Answer.condition,key) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),SD=sd(rt),Var=var(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

response_time = ggplot(agr, aes(fill=key,x=Answer.condition,y=Mean)) +
  geom_bar(stat="identity",position=position_dodge(.9)) +
  scale_fill_manual(values = key_col) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25,position=position_dodge(.9)) +
  ylab("mean rawRT")+
  xlab("")+
  labs(fill="response") +
  #geom_point(data=agr2, aes(color = as.factor(workerid)),alpha=.2) +
  #geom_line(data=critical, aes(y = rt, group= as.factor(workerid),color = as.factor(workerid)),alpha=.2)+
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3)

response_time

#ggsave(response_time, file="../graphs/response_time.pdf",width=6,height=3.5)
```

**Response time, trial order and QUD**

```{r response_time_order, echo=FALSE, fig.height=3, fig.width=9}
order = critical %>%
  group_by(slide_type,key,Answer.condition) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),SD=sd(rt),Var=var(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(slide_type_rename = ifelse(slide_type=="trial_1","first_half", ifelse(slide_type=="trial_2", "second_half", slide_type)))

ggplot(order, aes(fill=key,x=Answer.condition,y=Mean)) +
  geom_bar(stat="identity",position=position_dodge(.9)) +
  scale_fill_manual(values = key_col) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25,position=position_dodge(.9)) +
  ylab("mean rawRT")+
  xlab("")+
  labs(fill="response") +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  facet_grid(~slide_type_rename)
```

**Response time, responder type and QUD**

```{r response_time_responder, echo=FALSE, fig.height=4, fig.width=8}
responder = critical %>%
  group_by(workerid,key, .drop=FALSE) %>%
  count(key) %>%
  filter(key=="Yes") %>%
  mutate(responder_type = ifelse(n>4,"semantic",ifelse(n<4,"pragmatic",ifelse(n==4,"inconsistent","NA"))))

agr2 = critical %>%
  merge(responder[ ,c("workerid","responder_type")], by="workerid",all.x=TRUE) %>%
  group_by(Answer.condition,key,responder_type) %>% 
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),SD=sd(rt),Var=var(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) #%>%
  #filter(responder_type != "inconsistent")

responder2 = ggplot(agr2, aes(fill=key,x=Answer.condition,y=Mean)) +
  geom_bar(stat="identity",position=position_dodge(.9)) +
  scale_fill_manual(values = key_col) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25,position=position_dodge(.9)) +
  xlab("") +
  labs(fill="response") +
  facet_grid(~responder_type)+
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3)

responder2

#ggsave(responder, file="../graphs/responder.pdf",width=8,height=4)

```

**Response time, age and QUD**

```{r response_time_age, echo=FALSE, fig.height=4, fig.width=8}
agr3 = critical %>%
  merge(demo[ ,c("workerid","age")], by="workerid",all.x=TRUE) %>%
  mutate(age_bucket = ifelse(age<=25,"18-25",ifelse(age<44,"26-44", ifelse(age>44,"45+",NA)))) %>%
  group_by(Answer.condition,key,age_bucket) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),SD=sd(rt),Var=var(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  filter(!age_bucket == "NA") %>%
  filter(!age_bucket == "26-44")

age_time= ggplot(agr3, aes(fill=key,x=Answer.condition,y=Mean)) +
  geom_bar(stat="identity",position=position_dodge(.9)) +
  scale_fill_manual(values = key_col) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25,position=position_dodge(.9)) +
  theme(plot.title = element_text(hjust =0.5),axis.text.x=element_text(angle=45,hjust=1,vjust=1))+
  xlab("") +
  labs(fill="response") +
  facet_wrap(~age_bucket, scales="free_y") +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3)

age_time

#ggsave(age_time, file="../graphs/age_time.pdf",width=8,height=4)
```

**Response time, age, responder type and QUD**

```{r response_time_age_responder, echo=FALSE}
agr2 = critical %>%
  merge(responder[ ,c("workerid","responder_type")], by="workerid",all.x=TRUE) %>%
  merge(demo[ ,c("workerid","age")], by="workerid",all.x=TRUE) %>%
  mutate(age_bucket = ifelse(age<=25,"0-25",ifelse(age<44,"26-44", ifelse(age>44,"45+",NA))))%>%
  group_by(Answer.condition,key,responder_type,age_bucket) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),SD=sd(rt),Var=var(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(agr2, aes(fill=key,x=Answer.condition,y=Mean)) +
  geom_bar(stat="identity",position=position_dodge(.9)) +
  scale_fill_manual(values = key_col) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.25,position=position_dodge(.9)) +
  xlab("") +
  labs(fill="response") +
  facet_grid(age_bucket~responder_type)+
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3)
```

**Models**
```{r models1, eval=FALSE, include=FALSE}
library(lme4)
library(languageR)
library(brms)

# Mixed effects logistic regression predicting response type with random by-participant intercepts, from fixed effects of QUD
m = glmer(key ~ Answer.condition + (1|workerid), data=critical, family="binomial")
summary(m)

#BRMS 
#key should be 0 and 1, than center???
critical = critical %>%
  mutate(numericKey = ifelse(key == "Yes",1,0))

View(critical)

m_brms = brm(key ~ Answer.condition + (1|workerid), save_all_pars=TRUE, data=critical, iter=1000, family="binomial") #or gaussian
summary(m_brms)

# Mixed effects linear regression model with random by-participant intercepts predicting log-transformed response time from fixed effects of QUD, response type and their interaction
m2=lmer(logRT ~ Answer.condition*key + (1|workerid), data=critical)
summary(m2)

#EXTRA
# same models with responder type (and maybe age?)
critical_new = critical %>%
  merge(responder[ ,c("workerid","responder_type")], by="workerid",all.x=TRUE) %>%
  merge(demo[ ,c("workerid","age")], by="workerid",all.x=TRUE)
View(critical_new)

m3 = glmer(key ~ Answer.condition*responder_type + (1|workerid), data=critical_new, family="binomial")
summary(m3)

m4 = lmer(logRT ~ Answer.condition*responder_type*key + (1|workerid), data=critical_new)
summary(m4)
```

